\section{Etherless-Server}
	
	\subsection{Getting started}
		The implementation details of the Etherless-server module are presented in this section of the document.
	
		\subsubsection{Technologies} %Elencare le tecnologie utilizzate in questo modulo. La descrizione spetta al Glossario appendice!
			\subsubsubsection{Languages}
				\begin{itemize}
					\item Typescript; 
					\item Javascript.
				\end{itemize}
			\subsubsubsection{Utilities}
				\begin{itemize}
					\item Visual Studio Code;
					\item npm; 
					\item node.js;
					\item ts-node;
					\item AWS Lambda;
					\item AWS Elastic Beanstalk;
					\item IPFS;
					\item ESLint;
					\item Serverless Framework;
					\item mocha.
				\end{itemize}
			\subsubsubsection{Libraries}
				\begin{itemize}
					\item ethers.js;
				\end{itemize}
		
		\subsubsection{Requirements} %Requisiti necessari, suddivisi tra hardware e software.
			\subsubsubsection{Hardware}
				No specific hardware requirements are required for this module.
			\subsubsubsection{Software}
				To use the services provided by Amazon Web Services, an AWS account is required.
		
		\subsubsection{Setup} %Step da seguire per configurare correttamente il modulo
		
		\subsubsection{Enviroments} % (?Necessario?)
		
		\subsubsection{Functionality} %Funzionalità e comandi messi a disposizione dal modulo. Dividerle in sottosezioni!
			\subsubsubsection{Run}
				\subsubsubsection*{Utility}
					This feature allows the user to interact and execute functions previously loaded by a developer.
				\subsubsubsection*{Command}
					
			\subsubsubsection{Deploy}
				\subsubsubsection*{Utility}
					This feature allows developers to upload functions on AWS Lambda, ready to be invoked by a user.
				\subsubsubsection*{Command}
				
			\subsubsubsection{Edit}
				\subsubsubsection*{Utility}
					This feature allows the developer to edit functions previously loaded into the server.
				\subsubsubsection*{Command}
				
			\subsubsubsection{Delete}
				\subsubsubsection*{Utility}
					This feature allows the developer to delete functions previously loaded into the server.
				\subsubsubsection*{Command}
	
	
	\subsection{Developer's guide}
	
		\subsubsection{Architecture} % Descrizione dell'architettura utilizzata, compresi i design pattern
		
		\subsubsection{Method} %Descrizione accurata dei metodi presenti nel modulo
			\subsubsubsection{SmartManager}
			\subsubsubsection{Controller}
			\subsubsubsection{AWSManager}
			\subsubsubsection{IPFSManager}
			
		
		\subsubsection{Extensions}  %Possibili sviluppi futuri