\section{Glossary}

	\subsection*{\fbox{B}}
		\subsubsection*{Blockchain}
			A blockchain is a growing list of records, called blocks, that are linked using cryptography. Usually this data is shared among computers that are linked through a peer to peer network. 

	\subsection*{\fbox{C}}
		\subsubsection*{Cli}
			Command line interface is a type of user interface that only uses text for the communication between the user and the computer. In a CLI each textual input corresponds to a specific action.
		
		\subsubsection*{Cloud}
			A term that refers to the technology that allows you to process, store and transmit data on the network, using services on demand. In particular, the term "Cloud" generally refers to the remote hardware where this data is processed.

	\subsection*{\fbox{E}}
		\subsubsection*{Ethereum}
			Open-source software platform based on blockchain$_{G}$ technology that enables developers to build and deploy decentralized applications. 
			
		\subsubsection*{Ether}
			Cryptocurrency used in the Ethereum$_{G}$ network. 
	
	\subsection*{\fbox{G}}
		\subsubsection*{Git}
			A distributed version-control system for tracking changes in source code during software development.
			
	\subsection*{\fbox{M}}
		\subsubsection*{Mnemonic phrase}
			Also called mnemonic recovery phrase, it is a list of words which store all the information needed to recover a cryptocurrency wallet.
	
	\subsection*{\fbox{N}}
		\subsubsection*{Node.js}
			Javascript framework used for building applications. 
	
	\subsection*{\fbox{P}}
		\subsubsection*{Private key}
			A private key is a sophisticated form of cryptography that allows a user to access their cryptocurrency. Its security helps to protect a user from theft and unauthorized access to funds.
	
	\subsection*{\fbox{S}}
		\subsubsection*{Serverless Framework}
			A free and open-source web framework written using Node.js for building applications on AWS Lambda.
			
		\subsubsection*{Smart contract}
			A computer program or a transaction protocol, which is intended to automatically execute, control or document legally relevant events and actions according to the terms of a contract, an agreement or a negotiation.