\section{Product installation and setup}
  \subsection{Requirements}
    This section describes all of the basic requirements needed to run and test the product.
    \subsubsection{Hardware requirements}
      \begin{itemize}
      	\item \textbf{Internet connection}: needed for the interaction with the Ethereum$_{G}$ blockchain$_{G}$ and AWS.
      \end{itemize}
    \subsubsection{Software requirements}
      \begin{itemize}
        \item \textbf{Node.js$_{G}$:} version 12.0.0 or higher is required. Download and install the latest version from the \href{https://nodejs.org/it/download/}{Node official site};
        \item \textbf{npm (Node Package Manager):} version 6.10.0 or higher is required. It comes with the installation of Node.
        \item \textbf{Git$_{G}$:} a working version of git that can be found at \href{https://git-scm.com/book/en/v2/Getting-Started-Installing-Git}{How to install Git}.
      \end{itemize}
    \subsubsection{General requirements}
      In order to interact with the Ethereum$_{G}$ network an Ethereum$_{G}$ account is needed. The account needs to have a positive balance so that functionality costs can be covered. With \textit{Etherless} a wallet on the run can be created, but it does not contain any Ethers$_{G}$.
  \subsection{Installation}
    The following instructions are to be intended for use on a Unix-based system. Instructions for use on different systems will be added in the future.
    \subsubsection{Download the application}
    You can intall \textit{Etherless} by opening a terminal window and running the command:
     \begin{center}
     \code{npm i @roundabout-team/etherless-cli -g}
     \end{center}
     Depending on your Operating System, administrator privileges may be required. \\
         \subsubsection{Usage}
      To run \textit{Etherless}, just open a terminal window after completing the installation process. You will use specific commands to execute \textit{Etherless} features. Such commands are described in details in the next section.
