\section{Troubleshooting errors}
Below you can find a list of errors you may get while using \textit{Etherless}, their meaning and how to solve them.
  %This section describes the various error messages that may appear while using the application. %These errors may derive either from improper use of the commands or from other issues.
  %\subsection{Installation}
    %While installing \textit{Etherless}, some errors may occur:
    %\begin{itemize}
     % \item \textbf{npm ERR! code EEXIST:} the package manager is unable to run the \texttt{npm link} command. In the same folder run \texttt{npm unlink} and run \texttt{npm link} again.
   % \end{itemize}
  \subsection{Account management errors}
    \begin{itemize}
      \item \textbf{"No user logged in":} you are trying to run \textit{Etherless} commands while not being logged into the platform. To solve this error, log in before executing \textit{Etherless} commands;
      \item \textbf{"You are already logged in":} you are already logged in and can use the \textit{Etherless} platform;
      \item \textbf{"You are already logged out":} you are already logged out from the \textit{Etherless} platform.
    \end{itemize}
    
    \subsection{Generic errors}
    \begin{itemize}
    		\item \textbf{"Invalid password":} the password you inserted to decrypt your wallet is not the one you chose when you logged in;
    		\item \textbf{"Non-existing or no command specified":} the command you inserted does not exist.
    \end{itemize}
  
  \subsection{Login errors}
  \begin{itemize}
  	\item \textbf{"Hex string must have 0x prefix" or "Invalid hexadecimal string":} this error indicates that when logging in the private key$_{G}$ was not recognised, possibly due to incorrect format. Check your key again and retry.
  	\item \textbf{"Invalid mnemonic":} the mnemonic phrase inserted is not valid.
  \end{itemize}
    
  \subsection{Run errors}
  \begin{itemize}
    \item \textbf{"The function you are looking for does not exist":} no function with the given name exists in \textit{Etherless}. Check you typed in the correct function name and try again;
     \item \textbf{"The number of parameters is not correct":} the number of parameters you inserted to execute the function does not match the number of parameters required by the function to properly execute. You can use the \texttt{info} command to get detailed information about the correct parameters you need to insert for proper execution;
      \item \textbf{"Insufficient funds":} the amount of Ether you sent is not sufficient for executing the function. You can check the function price by using the \texttt{info} command.
  \end{itemize}
  
  \subsection{Deploy errors}
  \begin{itemize}
    \item \textbf{"The name of the function is already used":} a function with the same name already exists in \textit{Etherless}. Change the name or deploy a different function;
    \item \textbf{"ENOENT: no such file or directory, lstat '[path]'":} the file containing the code of the function to be deployed was not found in the given path. Check that the given path is correct and contains the function file;
    \item \textbf{"No function [name] found in file":} the name of the function inserted in the command must be the same present in the file;
    \item \textbf{"The source file must be a Javascript file":} only Javascript functions can be deployed on the platform ;
    \item \textbf{"The name must be at most 30 characters long":} the name of the function must be at most 30 characters long;
    \item \textbf{"The description must be at most 150 characters long":} the description of the function must be at most 150 characters long;
    \item \textbf{"Unexpected token ([line];[row])":} there is a syntax error in the Javascript file. You should correct it to deploy the function; 
    \item \textbf{"Insufficient funds":} the amount of Ether you sent is not sufficient for deploying the function.
  \end{itemize}
  
  \subsection{Edit errors}
  \begin{itemize}
   \item \textbf{"The function you are looking for does not exist":} no function with the given name exists in \textit{Etherless}. Check you typed in the correct function name and try again;
    \item \textbf{"You are not the owner of the function":} you can only edit function you own. Try checking if you are logged with the correct profile using \texttt{whoami} command;
    \item \textbf{"ENOENT: no such file or directory, lstat '[path]'":} the file containing the code of the function to be edited was not found in the given path. Check that the given path is correct and contains the function file;
     \item \textbf{"The source file must be a Javascript file":} only Javascript functions can be deployed on the platform so if you want to edit a function you must provide a Javascript source file;
    \item \textbf{"The name must be at most 30 characters long":} the name of the function must be at most 30 characters long;
    \item \textbf{"The description must be at most 150 characters long":} the description of the function must be at most 150 characters long;
    \item \textbf{"Unexpected token ([line];[row])":} there is a syntax error in the Javascript file. You should correct it to edit the function; 
    \item \textbf{"Insufficient funds":} the amount of Ether you sent is not sufficient for editing the function.
  \end{itemize}
  
  \subsection{Delete errors}
  \begin{itemize}
    \item \textbf{"You are not the owner of the function":} the function you are trying to delete is not yours. You can only delete one of the functions you deployed;
    \item \textbf{"The function you are looking for does not exist":} the function you are trying to delete is not present on the \textit{Etherless} platform.
  \end{itemize}
  
  \subsection{Info errors}
  \begin{itemize}
    \item \textbf{"The function you are looking for does not exist":} no function with the given name exists in \textit{Etherless}.
  \end{itemize}
